Improving the Replicability of Psychological Science Through Pedagogy

### 2016-09-23 paper/paper.Rmd
remove https:// from table

\begin{table}[ht]
\footnotesize
\centering
\begin{tabular}{lllllr|lrcl}
  \hline
\specialcell{Citation\\(Psychological Science; 2015)} & Expt. & \specialcell{Open\\Data?} & \specialcell{Open\\Materials?} & \specialcell{On\\MTurk?} & \specialcell{N\\(orig)} & \specialcell{Power\\Standard} & \specialcell{N\\(rep)} & \specialcell{Instructor\\Fidelity} & \specialcell{Project link} \\ 
  \hline
Atir, Rosenzweig, \& Dunning & 1b & No & Yes & Yes & 202 & Other &  50 & 6.67 & https://osf.io/uegk5/ \\ 
Ko, Sadler, \& Galinksy & 2 & Yes & Some & No &  40 & Original &  40 & 4.67 & https://osf.io/g6k2u/\\ 
Lewis \& Oyserman & 4 & No & Yes & Yes & 122 & 80\% power & 128 & 6.67 & https://osf.io/rdw6e/ \\ 
Liverence \& Scholl & 1 & No & Some & No &  18 & Original* &  19 & 5.33 & https://osf.io/sfxrb/ \\ 
Proudfoot, Kay, \& Koval & 1 & No & No & Yes &  80 & 80\% power &  84 & 6.67 & https://osf.io/ne8ph/ \\ 
Scopelliti, Loewenstein, \& Vosgerau & 3 & Yes & Yes & Yes & 550 & Other & 124 & 5.67 & https://osf.io/32wsm/ \\ 
Sofer et al. & 1 & No & Yes & No & 48 & Other &  95 & 4.33 & https://osf.io/5wmhn/ \\ 
Storm \& Stone & 3 & No & No & No & 48 & Original &  61 & 4.00 & https://osf.io/9cgpq/ \\ 
Wang et al. & 2 & No & No & No & 219 & 80\% power & 397 & 4.33 & https://osf.io/ng96w/ \\ 
Xu \& Franconeri & 1a & No & No & No &  12 & Other* &  27 & 5.00 & https://osf.io/cgvzs/ \\ 
Zaval, Markowitz, \& Weber & 1 & Yes & Yes & Yes & 312 & Original & 321 & 5.00 & https://osf.io/degwa/ \\ 
   \hline
\end{tabular}
\caption{\label{tab:summary} Summary characteristics of original studies and our replications, along with links to project pages for individual projects. * marks projects where the number of trials was modified.} 
\label{tab:summary}
\end{table}

>>>>

\begin{table}[ht]
\footnotesize
\centering
\begin{tabular}{lllllr|lrcl}
  \hline
\specialcell{Citation\\(Psychological Science; 2015)} & Expt. & \specialcell{Open\\Data?} & \specialcell{Open\\Materials?} & \specialcell{On\\MTurk?} & \specialcell{N\\(orig)} & \specialcell{Power\\Standard} & \specialcell{N\\(rep)} & \specialcell{Instructor\\Fidelity} & \specialcell{Project link} \\ 
  \hline
Atir, Rosenzweig, \& Dunning & 1b & No & Yes & Yes & 202 & Other &  50 & 6.67 & osf.io/uegk5/ \\ 
Ko, Sadler, \& Galinksy & 2 & Yes & Some & No &  40 & Original &  40 & 4.67 & osf.io/g6k2u/\\ 
Lewis \& Oyserman & 4 & No & Yes & Yes & 122 & 80\% power & 128 & 6.67 & osf.io/rdw6e/ \\ 
Liverence \& Scholl & 1 & No & Some & No &  18 & Original* &  19 & 5.33 & osf.io/sfxrb/ \\ 
Proudfoot, Kay, \& Koval & 1 & No & No & Yes &  80 & 80\% power &  84 & 6.67 & osf.io/ne8ph/ \\ 
Scopelliti, Loewenstein, \& Vosgerau & 3 & Yes & Yes & Yes & 550 & Other & 124 & 5.67 & osf.io/32wsm/ \\ 
Sofer et al. & 1 & No & Yes & No & 48 & Other &  95 & 4.33 & osf.io/5wmhn/ \\ 
Storm \& Stone & 3 & No & No & No & 48 & Original &  61 & 4.00 & osf.io/9cgpq/ \\ 
Wang et al. & 2 & No & No & No & 219 & 80\% power & 397 & 4.33 & osf.io/ng96w/ \\ 
Xu \& Franconeri & 1a & No & No & No &  12 & Other* &  27 & 5.00 & osf.io/cgvzs/ \\ 
Zaval, Markowitz, \& Weber & 1 & Yes & Yes & Yes & 312 & Original & 321 & 5.00 & osf.io/degwa/ \\ 
   \hline
\end{tabular}
\caption{\label{tab:summary} Summary characteristics of original studies and our replications, along with links to project pages for individual projects. * marks projects where the number of trials was modified.} 
\label{tab:summary}
\end{table}
